\documentclass[letter,10pt]{scrartcl}
\raggedright
\usepackage[paperwidth=8.5in,paperheight=11.0in,margin=0.85in]{geometry}
%\usepackage[urw-garamond]{mathdesign}
%\usepackage[scaled]{helvet}
\usepackage[default]{sourcesanspro}
\usepackage[T1]{fontenc}
\usepackage{enumitem}
\setlist{nolistsep,noitemsep,leftmargin=1em,label=--}
\begin{document}
\pagestyle{empty}
\raggedright
%\setlength{\parindent}{2em}
%\begin{tabularx}{\textwidth}{lXr}
  %\multirow{4}{*}{\Huge \textsf{\textbf{Alexander C. Rucker}}} 
  %%&&\texttt{acrucker@stanford.edu} \\ 
  %&&\textsc{acrucker@stanford.edu} \\ 
  %&& (732) 470-5808 \\ 
  %&& 5 Comstock Cir., 401A \\ 
  %&& Stanford, CA 94305-7710
%\end{tabularx}
\parbox{4in}{
  \vfill
  \Huge \textsf{\textbf{Matthew Vilim}}\\
  \vfill
}\hfill
\parbox{1.75in}{
  \centering
  \textsc{mvilim@stanford.edu} \\
(331) 643-9982 \\
488 Winslow St. \\
Apt 416 \\
Redwood City, CA 94063
} 

\newcommand{\entry}[3]{%
  \hfill%
  \parbox{1.6in}{\raggedleft\vfill{\large \textbf{#1}}\\#2\vfill}%
  \hskip 0.25in%
  \parbox{4.9in}{\raggedright\vfill#3\vfill}%
  \hfill%
  \vskip 1.0em %
}

\newcommand{\lineitem}[3]{%
  \parbox{1.2in}{#2}\hskip 0.10in%
  \parbox{1.1in}{\raggedright\textbf{#1}}\hskip 0.10in%
  \parbox{4.25in}{#3}\hfill\\[0.2em]%
}

%\newcommand{\listit}{\rule[0.65ex]{0.5em}{0.25ex}\hskip 0.5em}
\newcommand{\listit}{\raisebox{0.1ex}{--}\hskip 0.5em}
\newcommand{\header}[1]{%
  \vskip 1.0em %
  {\Large %
    \leavevmode{\leaders\hrule height.5ex depth\dimexpr-.5ex+0.4pt\hfill%
    %\hskip 0.5em \hbox{\textsc{#1}} \hskip 0.5em %
    \hskip 0.5em \hbox{{#1}} \hskip 0.5em %
    \leaders\hrule height.5ex depth\dimexpr-.5ex+0.4pt\hfill}
  }%
  %{\Large \hrulefill\hskip 0.5em{\textsc{#1}}\hskip 0.5em\hrulefill \\%
  \vskip 0.75em%
}

\header{Education}
\entry{Stanford University}{
  PhD, Electrical Eng. \\
  Jan 2017 -- Present
}{
  \begin{itemize}
    \item Advised by {Kunle Olukotun} \hfill GPA: \textbf{4.07}
    \item Language, compiler, and architecture design of reconfigurable accelerators for data analytics and ML.
  \end{itemize}
}
\entry{Stanford University}{
  MS, Electrical Eng. \\
  Sep 2016 -- March 2018
}{
  \hfill GPA: \textbf{3.95}
}
\entry{U of I (UIUC)}{
  BS, Computer Eng. \\
  Aug 2012 -- Dec 2015

}{
  \begin{itemize}
    \item Highest Honors \hfill GPA: \textbf{3.95}
    \item University Honors (top 3\% of College of Engineering)
  \end{itemize}
}

\header{Work Experience}
\entry{NVIDIA}{
  Santa Clara, CA\\
  GPU Hardware Verification Intern\\
  March 2016 -- Aug 2016
}{
  \begin{itemize}
    \item Contributed to features and performance of Volta randoms program generator
    \item Worked with architecture team to test and verify Volta memory model
  \end{itemize}
}
\entry{NVIDIA}{
  Santa Clara, CA\\
  Systems Software Intern\\
  Summers 2014, 2015
}{
  \begin{itemize}
    \item Developer on Mac OS X graphics drivers team
    \item Worked across all levels of the driver stack, including display and OpenGL drivers
    \item Ported features only implemented in Windows drivers to OS X drivers
  \end{itemize}
}
\entry{Argonne National Laboratory (ANL)}{
  Lemont, IL\\
  Research Intern\\
  Summers 2012, 2013
}{
  Developer on GREET (greet.es.anl.gov), a model of U.S. emissions
}

\header{Research Experience}
\entry{Prof. Olukotun}{
  Stanford University \\
  Jan 2018 -- Present
}{
  \begin{itemize}
    \item Adapted booksim with a custom simulator to evaluate networks for CGRAs
    \item Wrote a genetic-algorithm based placement tool for hybrid networks
    \item Zhang, Y., \textbf{Rucker, A.}, \emph{et al.} ``Compiler-Directed Hybrid Networks for Spatial Architectures.'' \emph{ASPLOS, 2019.} (Submitted)
  \end{itemize}
}
\entry{Prof. Dally}{
  Stanford University \\
  Sep 2017 -- Dec 2017
}{
  \begin{itemize}
    \item Adapted boolean satisfiability algorithms to allow efficient hardware acceleration
    \item Performed ASIC place-and-route to quantify accelerator hardware requirements
    \item Zhu, C., \textbf{Rucker, A.}, Wang, Y., Dally, W.J. ``SATin: Hardware for Boolean Satisfiability Inference.'' \emph{HPCA, 2019.} (Submitted)
  \end{itemize}
}
\entry{Prof. Suh}{
  Cornell University \\
  Jan 2015 -- May 2017
}{
  \begin{itemize}
      \item Developed an online scheme to predict GPGPU kernel behavior and
            enable dynamic voltage and frequency scaling while meeting soft real-time
            deadlines
          \item Chen, T., \textbf{Rucker, A.}, Suh, G.E. 
          ``Execution Time Prediction for Energy-Efficient Hardware
          Accelerators.'' \emph{MICRO, 2015.}
  \end{itemize}
}

\header{Extracurricular Activities}
\lineitem{Long Hill FAS}{Oct 2012 -- May 2017}{
  \begin{itemize}
      \item Oversaw patient care on a 2--4 person BLS ambulance crew
      \item Received life saving award for CPR save (Jan 2016)
  \end{itemize}
}
\lineitem{Cornell EMS}{Jan 2015 -- May 2017}{
  \begin{itemize}
    \item EMT/Crew Chief with a 24/7 student-run BLS first response service
  \end{itemize}
}
\lineitem{HKN Treasurer}{May 2016 -- May 2017}{
  \begin{itemize}
      \item Helped organize tutoring for introductory classes and other events
  \end{itemize}
}
\lineitem{ECE 2400 TA}{Spring 2017}{
  \begin{itemize}
      \item TA'ed first offering of C/systems programming class
  \end{itemize}
}
\lineitem{DTD Risk Manager}{Jan 2016 -- Dec 2016}{
  \begin{itemize}
      \item Ensured guest safety during events and served as honor board chair
  \end{itemize}
}
\lineitem{Eng. Peer Advisor}{Fall 2015, Fall 2016}{
  \begin{itemize}
      \item Co-led weekly freshman seminar and provided advice about engineering
  \end{itemize}
}
\lineitem{ECE 3140 TA}{Spring 2016}{
  \begin{itemize}
      \item TA'ed embedded systems using new, ARM-based development boards
  \end{itemize}
}
\lineitem{ECE 2300 TA}{Fall 2015}{
  \begin{itemize}
      \item Redesigned digital logic labs to allow students to take them home
  \end{itemize}
}
\end{document}
